### 2012-03-28 contents.tex
Writing about the removal of mass verifications.

@@

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers who perform verifications at least 10 times more often than contribute bug fixes), and the proportion of bug verifications they account for. Mass verifications and developers who have not contributed with fixes and verifications are discarded from the analysis.

>>>>

	In the next two analyses (who and how), mass verifications were discarded. A verification was considered to be part of a mass verification if the developer who performed it also performed at least other 49 verifications in the same day. Although further research is needed to evaluate such criterion, it was able to identify the most obvious mass verification cases.

	After applying the criterion to identify mass verifications, 362 (2.4\%) verifications were discarded from Eclipse/Platform, 2348 (72.3\%) verifications were discarded from Eclipse/EMF, and 5336 (39.3\%) verifications were discarded from NetBeans/Platform. Mass verifications were not identified in NetBeans/VersionControl.

@@

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers who perform verifications at least 10 times more often than contribute bug fixes), and the proportion of bug verifications they account for. Mass verifications and developers who have not contributed with fixes and verifications were discarded from the analysis.
